Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging

### 2016-02-09 writeup/gz_hubble_data.tex
added images to goods analysis
updated some goods analysis

% Journals
%\newcommand{\mnras}{MNRAS}
%\newcommand{\apj}{ApJ}
%\newcommand{\apjl}{ApJL}
%\newcommand{\aj}{AJ}
%\newcommand{\pasp}{PASP}
%\newcommand{\aaps}{A\&AS}
%\newcommand{\aap}{A\&A}
%\newcommand{\apjs}{ApJS}
%\newcommand{\araa}{ARA\&A}
\newcommand{\pbar}{p_{\rm bar}}
\newcommand{\fHI}{f_{\rm HI}}

@@

\begin{table}
\caption{Distribution of \ferengi{} images analysed in Figure~\ref{fig:p_vs_p}. Correctable images had a single-valued relationship between their measured $p_{\rm features}$ values at high and low redshifts (white regions in Figure~\ref{fig:p_vs_p}). Uncorrectable images had a non single-valued relationship (green regions). NEI images had undetermined relationships due to a lack of data ($N<5$) in their corresponding sub-bins (purple regions).   \label{ferengi_corrections}}
\begin{tabular}{lrr}
\hline \hline
				                   & N       & \% \\
\hline 
Correctable                        & 1,884   & 48\% \\
Uncorrectable                      & 1,986   & 50\% \\
NEI                                & 80     &  2\%\\
Total                              & 3,950   & 100\% \\
\hline \hline
\end{tabular}
\end{table}

@@

\begin{table*}
\caption{Breakdown of what we can correct out of the Hubble data, by sample. \label{hubble_debiasable}}
\begin{tabular}{lrrrrrrrr}
\hline\hline
                                   & AEGIS   & COSMOS & GEMS & GOODS-N & GOODS-S & GOODS FULL   & SDSS    & Total \\
\hline
Correctable                        & 1,628   & 15,120 & 1,811 & 739    & 502     & 1,850	& 0       & 21,650\\
Uncorrectable                      & 1,869   & 26,184 & 2,407 & 524    & 1,115   & 2,670	& 0       & 34,769\\
No Correction Needed ($z \le 0.3$) & 944     & 11,781 & 1,193 & 258    & 258     & 1,083	& 37,545  & 53,062\\ 
NEI                                & 2,753   & 34,432 & 2,271 & 861    & 2,547   & 4,766	& 0       & 47,630\\
No Redshift Information            & 1,313   & 5,291  & 1,622 & 169    & 491     & 788		& 14,316  & 23,990\\
Total                              & 8,507   & 92,808 & 9,304 & 2,551  & 4,913   & 11,157	& 51,861  & 181,101\\
\hline\hline
\end{tabular}
\end{table*}

>>>>

% Journals
%\newcommand{\mnras}{MNRAS}
%\newcommand{\apj}{ApJ}
%\newcommand{\apjl}{ApJL}
%\newcommand{\aj}{AJ}
%\newcommand{\pasp}{PASP}
%\newcommand{\aaps}{A\&AS}
%\newcommand{\aap}{A\&A}
%\newcommand{\apjs}{ApJS}
%\newcommand{\araa}{ARA\&A}
\newcommand{\pbar}{p_{\rm bar}}
\newcommand{\pfeatures}{p_{\rm features}}
\newcommand{\fHI}{f_{\rm HI}}

@@

The unshaded regions in figure ~\ref{fig:p_vs_p} define discrete ranges of redshift, surface brightness, and $\pfeatures$ a galaxy must have in order for the $\zeta$ approach to be confidentely applied to a galaxy in the GZH sample. While the appropriate correctable regions were defined discretely, we assume the true correctable region is a smooth function of z, $\mu$, and $\pfeatures$. To define this smooth space, we use a convex hull method to enclose the correctable and uncorrectable \ferengi{} galaxies is z-$\mu$-$\pfeatures$ space. Due to scatter, the boundaries of the resulting hulls overlap. The boundaries are then adjusted until the contamination from both groups is minimized. We use the resulting hulls to define the correctable and uncorrectable regions for categorizing the Hubble galaxies. The results of this method and final categorization of the Hubble sample is displayed in Table~\ref{hubble_debiasable}. We find that of the galaxies at redshift higher than $z=z_{0}=0.3$, 17\% of these are able to be debiased using the $\zeta$ method, 27\% cannot be debiased, and 56\% cannot be determined, due to a lack of redshift or information or due to a lack of \ferengi{} data corresponding to those galaxies redshift/surface brightness values.

now talk about how we get low/high limits on pfeatures

\begin{table}ー
\caption{Distribution of \ferengi{} images analysed in Figure~\ref{fig:p_vs_p}. Correctable images had a single-valued relationship between their measured $p_{\rm features}$ values at high and low redshifts (white regions in Figure~\ref{fig:p_vs_p}). Uncorrectable images had a non single-valued relationship (green regions). NEI images had undetermined relationships due to a lack of data ($N<5$) in their corresponding sub-bins (purple regions).   \label{ferengi_corrections}}
\begin{tabular}{lrr}
\hline \hline
				                   & N       & \% \\
\hline 
Correctable                        & 1,884   & 48\% \\
Uncorrectable                      & 1,986   & 50\% \\
NEI                                & 80     &  2\%\\
Total                              & 3,950   & 100\% \\
\hline \hline
\end{tabular}
\end{table}

@@

\begin{table*}
\caption{Breakdown of what we can correct out of the GZH data, by sample. 
\label{hubble_debiasable}}
\begin{tabular}{lrrrrrrrr}
\hline\hline
                                  & AEGIS   & COSMOS & GEMS & GOODS-N & GOODS-S & GOODS FULL   & SDSS    & Total \\
\hline
Correctable                        & 1,628   & 15,120 & 1,811 & 739    & 502     & 1,850	& 0       & 21,650\\
Uncorrectable                      & 1,869   & 26,184 & 2,407 & 524    & 1,115   & 2,670	& 0       & 34,769\\
No Correction Needed ($z \le 0.3$) & 944     & 11,781 & 1,193 & 258    & 258     & 1,083	& 37,545  & 53,062\\ 
NEI                                & 2,753   & 34,432 & 2,271 & 861    & 2,547   & 4,766	& 0       & 47,630\\
No Redshift Information            & 1,313   & 5,291  & 1,622 & 169    & 491     & 788		& 14,316  & 23,990\\
Total                              & 8,507   & 92,808 & 9,304 & 2,551  & 4,913   & 11,157	& 51,861  & 181,101\\
\hline\hline
\end{tabular}
\end{table*}
